---
title: "The Production Possibilities Frontier Model"
output:
  html_notebook: default
  pdf_document: default
---

## Installation of required software

Please, execute the functions below to install and load the ***R*** package *Teaching Economics with R* (if you haven't done so already).

```{r installation, eval=FALSE, include=FALSE}
install.packages("devtools")
devtools::install_github("lyuben-ivanov/ter")

library(ter)
```

## Introduction to ppf_plot()

Please, type `ppf_plot()` in the code chunk below and execute the chunk to create a plot of the production possibilities frontier for a fictional country called Technopia that only produces two types of goods (pizzas and robots).

```{r}
ppf_plot()
```

As you can see from the plot above, the maximum amount of pizzas that Technopia can produce with its resources and the available technology is `50` mln per month (assuming that all the resources of the country are allocated for the production of pizzas). If Technopia allocates all its resources toward production of robots it will be able to produce a maximum amount of `50` thousand robots.

Let's learn how to use the `ppf_plot()` function in order to manipulate the graph of Technopia's production possibilities. As a first step, please clear the graph a little bit by removing point A. This can be done by entering value `FALSE` for the argument `plot_points` of the `ppf_plot` function as shown below. Please, execute the code chunk to see the result.

```{r}
ppf_plot(plot_points = FALSE)
```

Now, with some clutter removed, we can learn how to shift the production possibilities frontier by changing some arguments of the `ppf_plot()` function. The maximum amount of pizza that Technopia can produce can be changed by replacing the default value of the argument `new_maximum_quantity_of_product_1` with an integer ranging from `0` to `100`. The maximum amount of robots that Technopia can produce can be changed by replacing the default value of the argument `new_maximum_quantity_of_product_2` with an integer ranging from `0` to `50`. In the code chunk below you can try to shift the curve by changing the maximum quantity for any of the two products (or for both of them).

```{r}

```

Another important feature of `ppf_plot()` is the ability to choose the label and the location of the point that represents a possible combination of the two products that Technopia can produce for a given month. The location of the point on the graph is determined by the arguments `quantity_of_product_1` (an integer between `0` and `100`) and `quantity_of_product_2` (an integer between `0` and `50`). The label of point A can be changed by providing a different string (a few or more letters enclosed in parentheses) as a value of the argument `point_label` of `ppf_plot()`. Please use this information to show a combination of goods (e.g. `40` mln pizzas and `50 000` robots) that can not be produced by Technopia with the available resources and technology. Don't forget to change the label of the resulting point to "B".

```{r}
ppf_plot(quantity_product_1 = 40,
         quantity_product_2 = 50,
         point_label = "B")
```
